### 2005-01-24 doc/Simulation_and_Control_using_Supremica/automationobjects.tex
*** empty log message ***

%* AO consists of models, controllers, views and
%  configuration registry
Automation objects consists of models, controllers, views
and configuration registry implemented using IEC~61499
function blocks and their interfaces, see
figure~\ref{fig:AO}. Models are interchangeable simulation
models with varying level of abstraction. One model might
be used for the simulation on a high level of abstraction,
typically behavioral model, and another for the simulation
on a lower level. This is then used to implement dynamic
zooming during the simulation. One of the models will
implement the communication with the controlled equipment
thus allowing effortless switching between simulation and
actual control. This will enable gradual verification and
on-line tuning of the big automation systems by allowing the
simulation of the system components that are being
configured or tuned while running the components that are
already configured.
\begin{figure}[!ht]
  \centering
  \includegraphics{images/automationobjects/AO}
  \caption{The architecture of the automation object.}
  \label{fig:AO}
\end{figure}

>>>>

%* AO consists of models, controllers, views and
%  configuration registry
Automation objects consists of models, controllers, views
and configuration registry implemented using IEC~61499
function blocks, and their interfaces, see
figure~\ref{fig:AO}. Models are interchangeable simulation
models with varying level of abstraction. One model might
be used for the simulation on a high level of abstraction,
typically behavioral model, and another for the simulation
on a lower level. This is then used to implement dynamic
zooming during the simulation. One of the models will
implement the communication with the controlled equipment
thus allowing effortless switching between simulation and
actual control. This will enable gradual verification and
on-line tuning of the big automation systems by allowing the
simulation of the system components that are being
configured or tuned while running the components that are
already configured.
\begin{figure}[!ht]
  \centering
  \includegraphics{images/automationobjects/AO}
  \caption{The architecture of the automation object.}
  \label{fig:AO}
\end{figure}
